% -- Encoding UTF-8 without BOM
% -- XeLaTeX => PDF (BIBER)

\documentclass[print]{cv-style}          % Add 'print' as an option into the square bracket to remove colours from this template for printing. 
                                    % Add 'espanol' as an option into the square bracket to change the date format of the Last Updated Text

\sethyphenation[variant=british]{english}{} % Add words between the {} to avoid them to be cut 

\begin{document}

\header{Darshan }{Lukhi}           % Your name


%----------------------------------------------------------------------------------------
%	SIDEBAR SECTION  -- In the aside, each new line forces a line break
%----------------------------------------------------------------------------------------

\begin{aside}
%
\section{Contact}
40,Nandanvan society,
Chikuwadi,
Varachha Road,
Surat-395006
~
Mobile no:
+91 99092 92909
~
Email:-
darshanlukhi123
@gmail.com
%
\section{Languages }
{\vspace{0.1cm}}English,Hindi,
Gujarati(M.T)
%
\section{Programming
   Languages}
{\vspace{0.1cm}}{\color{red} $\varheartsuit$} Python, Node.Js
C, JAVA, C++,
C\# , PHP, MySQL
ASP .NET, JQuery
JavaScript, CSS
AJAX
%
\end{aside}


%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{comment}
\section{Experience}

\begin{entrylist}
%------------------------------------------------
\entry
  {2012-2013}
  {Aastha Solution Surat}
  {Surat, India}
  {\jobtitle{Trainee}\\
  One Year experience as Trainee of ASP.net and Java Developer in Aastha Solution Surat}
%------------------------------------------------
\entry
  {2014}
  {Sweetheart Fashion}
  {Surat, India}
  {\jobtitle{Trainee}\\
  Get two month training at Sweetheart Fashion Surat which are basically sales Ethelic Fashion wear Item on different E-Commerce Website like SnapDeal,Flipkart,Amazon and PayTm etc..\\\
  Detailed achievements:
  \begin{itemize}
    \item Get Detail understanding in E-commerce Website.
     
     \item Good Knowledge in CMS data Handling and 'HADOOP' Technology.
     
     
  \end{itemize}}
%------------------------------------------------
%------------------------------------------------

\end{entrylist}


\end{comment}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{Education}

\begin{entrylist}
%------------------------------------------------
\entry
{2016--2020}
{B.Tech {\normalfont in Computer Engineering(8.35 CPI)}}
{Dharmsinh Desai University}
{\vspace{-0.3cm}}
%------------------------------------------------
\entry
{2014--2016}
{HSC :- {\normalfont Ashadeep Vidhyalaya , Surat ( 84.20 \% ) }}
{GHSEB}
{\vspace{-0.3cm}}
\entry
{2013--2014}
{SSC :- {\normalfont Mangaldeep Vidhyalaya , Surat ( 83.83 \% )}}
{GSEB}
{}

%------------------------------------------------
\end{entrylist}

%----------------------------------------------------------------------------------------
%	OTHER QUALIFICATIONS SECTION
%----------------------------------------------------------------------------------------

\section{Projects}

\begin{entrylist}
%------------------------------------------------
\entry
{Apr-2019}
{Online Coding Competition }
{Angular 7 | Node.JS with Express Framwork | Ace.JS | MongoDB }
{\textbullet \,Its support intranet so its useful at collage level platform\newline 
\textbullet \,User can participate in various contests and solved problem of contest. \newline 
\textbullet\,Prepare IDE for compile and run code of  C, C++, Java and  Python.\newline
\textbullet\,User can view his solution and also able to see other user profile and solutions.\newline
\textbullet\,Admin can upload problem and manage contests by performing CRUD operations.}
{\vspace{-0.6cm}}
\end{entrylist}

\begin{entrylist}
%------------------------------------------------
\entry
{Apr-2019}
{Compiler Service }
{WCF Service | Angular 7 | Node.JS with Express Framwork }
{\textbullet\,Develop a Service for compile and execute the code for C, C++, Java and Python.\newline
\textbullet\,Create client in Angular 7 and Node.Js with Express which consume WCF Service. \newline
\textbullet\,Create client in C\# Windows Form Application  which consume WCF Service.}
{\vspace{-0.6cm}}
\end{entrylist}

%-----------------------------------------------
\begin{entrylist}
%------------------------------------------------
\entry
{ Oct-2018 }
{Customize Shoping }
{ASP .Net | MVC | C\# }
{\textbullet\,Provide a facility of customizable product options \& product bundling. 
\newline\textbullet\,Customization is available on Wears, whatches and glasses.
\newline\textbullet\,Provide search product functionality in the website.
}
{\vspace{-0.6cm}}
\end{entrylist}

\begin{entrylist}
%------------------------------------------------
\entry
{Oct-2018}
{Ask Anything }
{Angular 6 | HTML |CSS | Boostrap | JQuery | Javascript}
{\textbullet\,It is a platform like Quora, every user can ask question and give answer\newline 
\textbullet\,we create a frontend for login and register, choose category, ask question, give \newline\, \hspace*{0.5ex}  answer and view profile etc. and it is fully responsive}
{\vspace{-0.3cm}}
\end{entrylist}
\begin{entrylist}
%------------------------------------------------
\entry
{Mar-2018}
{Restaurant System}
{Python | DJango Framwork}
{
\textbullet\,Provide basic CRUD operation like as adding Foods and dishes.Changing/Updating \newline\, \hspace*{0.5ex} their price.\newline \textbullet\,A first  experience at making Website. The website provides very basic Functionality.}
{\vspace{-0.3cm}}


%------------------------------------------------
\end{entrylist}

%----------------------------------------------------------------------------------------
%	Achievement  SECTION
%----------------------------------------------------------------------------------------
\vspace{0.1cm}
\section{Achievements}

\begin{entrylist}
%------------------------------------------------
\entry
{}
{Secure 292th globally rank}
{}
{In  May Challenge 2019 Division 2 on the codechef}

%------------------------------------------------
\end{entrylist}

\begin{entrylist}
\entry
{}
{Full Score in SDP Subject}
{}
{get 10 out of 10 Credit in Software Devlopment Project  subject}

%------------------------------------------------
\end{entrylist}

\begin{entrylist}
\entry
{}
{Complete online course }
{}
{Completed MEAN Stack Developer course on edwisor.com }

%------------------------------------------------
\end{entrylist}



%----------------------------------------------------------------------------------------
%	INTERESTS SECTION
%----------------------------------------------------------------------------------------

\vspace{0.1cm}
\section{Interests}
  
\begin{entrylist}
%------------------------------------------------
\entry
{}
{Developing in Python and MEAN stack application}
{}
{Develop creative application in Python as well MEAN Stack}

\entry
  {}
  {Learn abut new Web technology }
  {}
  {\jobtitle{}Learn about the latest technology which helpful in company and Improve my
     programming Skills as well.}


\end{entrylist}\

  
%----------------------------------------------------------------------------------------
%	SKILLS SECTION
%----------------------------------------------------------------------------------------

\section{Skills}
  \vspace{-0.2cm}

\begin{entrylist}
%------------------------------------------------

%------------------------------------------------
\entry
  {}
  {Programming Ability }
  {}
  {\jobtitle{}Good programming skills in C++, JAVA, ASP .NET and python. }
  
  \entry
  {}
  {Knowledge of Git Version Control System }
  {}
  {\jobtitle{}My all project repository are available on Github 
   ( \jobtitle{https://github.com/DarshanLukhi/} )}
  
  \entry
  {}
  {Quick Learning Capability}
  {}
  {\jobtitle{}Quick learning all the fundamental of the Software Technology. }
  
  \entry
  {}
  {Good in Communication }
  {}
  {\jobtitle{}Know three different languages. }
  
%------------------------------------------------
%------------------------------------------------

\end{entrylist}

%----------------------------------------------------------------------------------------

%----------------------------------------------------------------------------------------
%	Hobby SECTION
%----------------------------------------------------------------------------------------


\end{document}